Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-10-14 Manuscript/manuscript.tex
Added/improved a list of MD simulations.

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations with
           numbers of individual molecules for each simulation
           at temperature $T$. 
         }
         \todo{SAMULI: Temperature column is not necessary because it is always the same.}
         \todo{SAMULI: Columns reporting the additional ion concentrations would be useful.}
         \todo{SAMULI: Order of the PC:PS (5:1)/Na+ systems in little bit confusing.}
\label{tbl:sim-list}
\begin{tabular}{l c c r r r r r }
  lipids/counter-ions &  \ce{K^+}  &  \ce{Na^+} & \ce{Ca^{2+}} & \ce{Cl^-} & \ce{H2O} &  PC:PS total  &  $T$~(K)  \\
  \hline
PC:PS (1:1)/Na+  &  0  &  64  &  0  &  0  &  5253  &  64:64  &  298 \\ 
PC:PS (1:1)/K+  &  64  &  0  &  0  &  0  &  5253  &  64:64  &  298 \\ 
PC:PS (10:1)/Na+  &  0  &  6  &  0  &  0  &  3600  &  60:6  &  298 \\ 
PC:PS (10:1)/K+  &  6  &  0  &  0  &  0  &  3600  &  60:6  &  298 \\ 
PC:PS (4:1)/Na+  &  0  &  12  &  0  &  0  &  3600  &  48:12  &  298 \\ 
PC:PS (4:1)/K+  &  12  &  0  &  0  &  0  &  3600  &  48:12  &  298 \\ 
PC:PS (5:1)/Na+  &  0  &  12  &  13  &  26  &  3561  &  60:12  &  298 \\ 
PC:PS (5:1)/Na+  &  0  &  12  &  26  &  52  &  3522  &  60:12  &  298 \\ 
PC:PS (5:1)/Na+  &  0  &  12  &  0  &  0  &  3600  &  60:12  &  298 \\ 
PC:PS (5:1)/K+  &  12  &  0  &  0  &  0  &  3600  &  60:12  &  298 \\ 
PC:PS (5:1)/Na+  &  0  &  12  &  39  &  78  &  3483  &  60:12  &  298 \\ 
PC:PS (5:1)/Na+  &  39  &  12  &  0  &  39  &  3483  &  60:12  &  298 \\ 
PC:PS (5:1)/Na+  &  0  &  51  &  0  &  39  &  3483  &  60:12  &  298 \\ 
  \hline
PS/K+  &  72  &  0  &  0  &  0  &  3600  &  0:72  &  298 \\ 
PS/Na+  &  0  &  72  &  0  &  0  &  3600  &  0:72  &  298 \\ 
  \hline
\end{tabular}
\end{table*}

>>>>

\begin{table*}[tbp]
\centering
\caption{  List of MD simulations reporting their respective
           added buffer concentrations,
           amounts of individual molecules,
           and the deployed models.
         }
\label{tbl:sim-list}
\begin{tabular}{l | r r r r | r r | c c }
                          &  \multicolumn{4}{c}{added buffer concentration / mM}    & \multicolumn{2}{c}{no. molecules} &  \multicolumn{2}{c}{simulated with model}  \\
PC:PS (ratio)/counterions &  \ce{K^+}  &  \ce{Na^+} & \ce{Ca^{2+}} & \ce{Cl^-}      & \ce{H2O} &  PC:PS                 &  ECC-lipids  &  Lipid17    \\
  \hline
PC:PS (0:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
PC:PS (0:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  0:72  &  X  &  X  \\ 
  \hline
PC:PS (10:1)/K+  &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
PC:PS (10:1)/Na+ &      0  &      0  &      0  &      0  &  3600  &  60:6  &  X  &  -  \\ 
  \hline
PC:PS (1:1)/K+   &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
PC:PS (1:1)/Na+  &      0  &      0  &      0  &      0  &  5253  &  64:64  &  X  &  X  \\ 
  \hline
PC:PS (4:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
PC:PS (4:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  48:12  &  X  &  -  \\ 
  \hline
PC:PS (5:1)/K+   &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &      0  &      0  &  3600  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &     78  &     78  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    125  &    125  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    202  &    202  &  3561  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    409  &    409  &  3522  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &      0  &    621  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &    621  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &   1510  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &      0  &   3002  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &    621  &      0  &      0  &    621  &  3483  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &   1510  &      0  &      0  &   1510  &  3377  &  60:12  &  X  &  X  \\ 
PC:PS (5:1)/Na+  &   3002  &      0  &      0  &   3002  &  3213  &  60:12  &  X  &  X  \\ 
  \hline
\end{tabular}
\end{table*}
